MINOS Handover Plots

### 2023-07-22 minos/validation/handovers.Rmd
Lots more WIP stuff on imputation and fixing var types in modules. Also added a testing notebook for comparing final_US, complete_US, and imputed stock data to influence decisions

>>>>

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.fsit <- raw.dat %>% 
  dplyr::select(pidp, time, financial_situation) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(financial_situation = mean(financial_situation, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.fsit <- base.dat %>%
  dplyr::select(pidp, time, financial_situation) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(financial_situation = mean(financial_situation, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
fsit <- rbind(raw.fsit, base.fsit)

# Now plot
ggplot(data = fsit, mapping = aes(x = time, y = financial_situation, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Financial Situation', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Average')

raw.fsit2 <- raw.dat %>% 
  dplyr::select(pidp, time, financial_situation) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(financial_situation = mean(financial_situation, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.fsit2 <- base.dat %>%
  dplyr::select(pidp, time, financial_situation) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(financial_situation = mean(financial_situation, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

fsit2 <- rbind(raw.fsit2, base.fsit2)

# Now plot
ggplot(data = fsit2, mapping = aes(x = time, y = financial_situation, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Financial Situation') +
  xlab('Year') +
  ylab('Average')

if (shall.we.save) {
  ggsave(filename = 'financial_situation_wav1.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.fsit, base.fsit, fsit, raw.wave1, raw.fsit2, base.fsit2, fsit2)
#rm(raw.phealth.check, base.phealth.check)
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, financial_situation)
base.s <- base.dat %>%
  select(pidp, age, time, financial_situation)

spaghetti_plot(spag, 'financial_situation',
             save = shall.we.save,
             save.path = save.path)
